### 2020-01-20 README.Rmd
try to shrink table

| Literature                | Package     | Reference     | Class Name      | mlr3 Sugar        |
| ---------------           | ---------   | ---------     | --------------- | ------------      |
| Spatial Buffering         | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBuffer`          | `rsmp("spcv-buffer")`          |
| Spatial Blocking          | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBlock`           | `rsmp("spcv-block")`           |
| Spatial CV                | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResamplingSpCVCoords`          | `rsmp("spcv-coords")`          |
| Environmental Blocking    | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVEnv`             | `rsmp("spcv-env")`             |
| ---                       | ---                                                       | ---           | ---                             | ---                            |
| Repeated Spatial Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `RepeatedResamplingSpCVBlock`   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV       | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `RepeatedResamplingSpCVCoords`  | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking     | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `RepeatedResamplingSpCVEnv`     | `rsmp("repeated-spcv-env")`    |

>>>>

| Literature                | Package     | Reference     | Class Name      | mlr3 Sugar        |
| ---------------           | ---------   | ---------     | --------------- | ------------      |
| Spatial Buffering         | blockCV     | Valavi 2019   | `ResamplingSpCVBuffer`          | `rsmp("spcv-buffer")`          |
| Spatial Blocking          | blockCV     | Valavi 2019   | `ResamplingSpCVBlock`           | `rsmp("spcv-block")`           |
| Spatial CV                | sperrorest  | Brenning 2012 | `ResamplingSpCVCoords`          | `rsmp("spcv-coords")`          |
| Environmental Blocking    | blockCV     | Valavi 2019   | `ResamplingSpCVEnv`             | `rsmp("spcv-env")`             |
| ---                       | ---         | ---           | ---                             | ---                            |
| Repeated Spatial Blocking | blockCV     | Valavi 2019   | `RepeatedResamplingSpCVBlock`   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV       | sperrorest  | Brenning 2012 | `RepeatedResamplingSpCVCoords`  | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking     | blockCV     | Valavi 2019   | `RepeatedResamplingSpCVEnv`     | `rsmp("repeated-spcv-env")`    |
